\chapter{Requirements Traceability}
 In this section is shown the mapping between the requirements stated in the RASD document and the component modules defined in this paper.
\\ \\
\textbf{[G1]The Registered User can access to the services offered by TrackMe System with a single account.}
\begin{itemize}
	\item Mobile Application: [R1 - R2]
	\item Web Application: [R3 - R4]
	\item AutomatedSOS Module: [R5]
\end{itemize} 

\textbf{[G2]The Registered User can be recognized by providing his/her username and password.}
\begin{itemize}
	\item Login Module (of Mobile Application): [R6] 
	\item Login Module (of Web Application): [R7]
\end{itemize} 

\textbf{[G3.1]Allow a User to manage the accesses to his/her personal data.}
\begin{itemize}
	\item Manage Request Module: [R8 - R9 - R10]
\end{itemize}

\textbf{[G3.2]Allow a User to visualize his/her actual health parameters and position.}
\begin{itemize}
	\item User Data Module: [R11 - R12 - R13]
\end{itemize} 

\textbf{[G3.3]Allow a User to visualize his/her past data history.}
\begin{itemize}
	\item User Data Module: [R14 - R15 - R15.1 - R16 - R16.1]
\end{itemize}

\textbf{[G3.4]Allow a Third Party to send an authorization request to a User for the access to the his/her data.}
\begin{itemize}
	\item Request Module:[R17 - R18 - R19]
	\item  Manage Request Module: [R20]
\end{itemize}

\textbf{[G3.4.1]Allow a Third Party to request the latest available data of a User.}
\begin{itemize}
	\item Data Module:[R21]
\end{itemize}

\textbf{[G3.4.2]Allow a Third Party to request a subscription to the data of a User.}
\begin{itemize}
	\item Request Module:[R22]
	\item Data Module : [R23]
\end{itemize}

\textbf{[G3.5]Allow a Third Party to request anonymized data of a set of Users.}
\begin{itemize}
	\item Request Module: [R24 - R25]
	\item Data Module : [R26]
\end{itemize}

\textbf{[G3.5.1]Allow the Third party to request the latest data of a set of Users.}
\begin{itemize}
	\item Data Module : [R27]
\end{itemize}

\textbf{[G3.5.2] Allow a Third Party to request a subscription to the data of a set of Users.}
\begin{itemize}
	\item Request Module:[R28]
	\item Data Module : [R29]
\end{itemize}

\textbf{[G3.6] Allow a Third Party to visualize the available data through useful statistics.}
\begin{itemize}
	\item Data Module : [R30]
\end{itemize}

\textbf{[G4.1] NHS is alerted when the User gets in a critical state.}
\begin{itemize}
	\item AutomatedSOS Module : [R31 - R32 - R33]
\end{itemize}

\textbf{[G4.2]Allow the User to create a list of contacts to be alerted in case of emergency.}
\begin{itemize}
	\item AutomatedSOS Module : [R34 - R35 - R36]
\end{itemize}

\textbf{[G5.1] Organizer can create a new run.}
\begin{itemize}
	\item Track4Run Module : [R37 - R38 - R39 - R40 - R41 - R42]
\end{itemize}

\textbf{[G5.2] Allow a User to enroll to a run as participant.}
\begin{itemize}
	\item Track4Run Module : [R43 - R44 - R45]
\end{itemize}

\textbf{[G5.3]Allow a User to visualize the list of scheduled runs.}
\begin{itemize}
	\item Track4Run Module : [R46 - R47 - R48]
\end{itemize}

\textbf{[G5.4] Allow a User to visualize the list of live runs.}
\begin{itemize}
	\item Track4Run Module : [R49 - R50]
\end{itemize}

\textbf{[G5.5] Allow a User to visualize on a map the positions of the participants
in a live run.}
\begin{itemize}
	\item Track4Run Module : [R51 - R52]
\end{itemize}