\section{Assumptions, dependencies and constraints}
Domain Assumptions:
\begin{enumerate}[label={[}D.\arabic*{]}]

\item \label{d:1}
The user owns a smart device connected to his/her smartphone.
\item\label{d:2}
The smart device collects the data through its sensors.
\item\label{d:3}
The device has regular internet connection.
\item\label{d:4}
The device has a working GPS system.
\item\label{d:5}
The GPS position has an accuracy of less than 5 mt.
\item\label{d:6}
An external map service will be used.
\item\label{d:7}
The map service is reliable.
\item\label{d:8}
Only registered users, either as third party or clients, can use the application.
\item\label{d:9}
At registration time, the user provides correct data: fiscal code, first name, last name, age, city, email, height and weight.
\item\label{d:10}
At registration time, the third party provides correct data: account holder, VAT number, address and email.
\item\label{d:11}
The device’s sensors send new data at least every 5 seconds.
\item\label{d:12}
After the start of an emergency, an ambulance will be dispatched at the user’s location as soon as possible.
\item\label{d:13}
For every urgent call, details about the emergency are correctly encoded.
\item\label{d:14}
The threshold value for emergency detection is provided by a trusted medical authority.
\item\label{d:16}
The map service provides only feasible paths accessible by foot.
\end{enumerate}

\vspace{10mm}

\textbf{Constraints:}

\begin{enumerate}
    \item\label{c:1} A group request can be executed only if there are at least 1000 users that match the requested characteristics.
    \item\label{c:2}
    From the time the parameters exceed a fixed threshold, the communication with NHS must be established within 5 seconds.
    \item\label{c:3}
    The subscription to a run is closed if the maximum number of participants is reached.
    \item\label{c:4}
    The mobile application must be able to store the data collected by the smart device, so that new data can be sent with a frequency that is lower than the one by which new data are generated. This ensures no loss of data in case of missing internet connection, as well as a lower battery consumption. 
\end{enumerate}


