\section{Purpose}
The purpose of this document is to provide a complete description of the TrackMe System, through the analysis of the problems, the listing and presentation of the goals, constraints, phenomena, domain assumptions and models with the aim of provide to the stakeholders a complete overview of the project. TrackMe provides three main services: Data4Help, AutomatedSOS and Track4run.

\vspace{10mm}

\begin{enumerate}[label={[}G\arabic*{]}]
\item \label{goal:trackme1} The Registered User can access to the services offered by TrackMe System with a single account.
    
    \item \label{goal:trackme2}The Registered User can be recognized by providing his/her username and password.
    
    
\end{enumerate}

\textbf{Goals of Data4Help:}
\begin{enumerate}[label={[}G3.\arabic*{]}]

    \item \label{goal:user1}Allow a User to manage the accesses to his/her personal data.
    \item \label{goal:user2}Allow a User to visualize his/her actual health parameters and position.
    \item \label{goal:user3}Allow a User to visualize his/her past data history.

    \item \label{goal:parties1}Allow a Third Party to send an authorization request to a User for the access to his/her data.
    
    \begin{enumerate}[label={[}G3.4.\arabic*{]}]
        \item \label{goal:parties2}Allow a Third Party to  request the latest available data of a User.
        \item \label{goal:parties3}Allow a Third Party to request a subscription to the data of a Users.
    \end{enumerate}

    \item \label{goal:parties4}Allow a Third Party to request anonymized data of a set of Users.
    
     \begin{enumerate}[label={[}G3.5.\arabic*{]}]
        \item \label{goal:parties5}Allow a Third Party to request the latest available data of the set of Users.
        \item \label{goal:parties6}Allow a Third Party to request a subscription to the data of the set of Users.
    \end{enumerate}
    
    \item \label{goal:parties7}Allow a Third Party to visualize the available data through useful statistics.
    \newline
    
\end{enumerate}

\textbf{Goals of AutomatedSOS}:
\begin{enumerate}[label={[}G4.\arabic*{]}]

\item \label{goal:sos1}NHS is alerted when the User gets in a critical state.
\item \label{goal:sos2}Allow the User to create a list of contacts to be alerted in case of emergency.
    
\end{enumerate}

\textbf{Goals of Track4Run}:
\begin{enumerate}[label={[}G5.\arabic*{]}]

    \item \label{goal:run1}Organizers can create a new run.
    \item \label{goal:run2}Allow a User to enroll to a run as participant.
    \item \label{goal:run3}Allow a User to visualize the list of scheduled runs.
     \item\label{goal:run4}Allow a User to visualize the list of live runs.
    \item \label{goal:run5}Allow a Users to visualize on a map the positions of the participants in a live run.
   
    
\end{enumerate}
