\subsection{Scenarios:}
\textbf{Scenario A} \\ \\
Tom is a middle age man who wants to keep an healthy lifestyle. He  decides to go to work on foot, to walk at least 10000 steps for day. Through TrackMe System, he can visualize his actual and past health data, and check if he reaches his daily goal. \\ \\
\textbf{Scenario B} \\ \\
Happy Company is a medical association registered as Third Party to TrackMe System, which exploit the Data4Help System to offer a new service to their patients which already use Track me or decide to sign up to the System . The patients which accept the company's subscription request about health data are monitored daily, and the collected data are stored in their personal medical records. During the examinations, those data are consulted by the doctors to complete the patient switchboard. \\ \\
\textbf{Scenario C} \\ \\
Data Corporation is a company interested in huge amount of data to make statistical analysis on different sets of individuals, based on different parameters e.g. age range, gender, city where they come from. It is registered to Track me System as Third party and use the System as an interesting database to query for their purposes, performing periodically anonymous researches on groups and studying the data that receives. \\ \\
\textbf{Scenario D} \\ \\
John is an elderly cardiopath man who are walking in the street. He's going to buy the newspaper like every morning. 
John has received as Christmas's gift from his son a smartwatch. His son has provided to register him to TrackMe service, to enable AutomatedSos System and added himself as emergency contact, to  take care of the father's health status in case of emergency.
Suddenly that morning John feels bad and falls to the ground. The sensors of his smartwatch detect an abnormal health status,probably an heart attack, and AutomatedSos starts the Emergency procedure, connecting to the nearest emergency ward, communicating the location and the health status of John and asking for an ambulance. His son is notified. The ambulance arrives after 5 minutes from the call and the doctors take care of him. \\ \\
\textbf{Scenario E} \\ \\ 
The mayor of an italian city wants to organize a city run. She decides to manage the event through Track4Run, inviting the interested citizens to sign up to the run. She selects the day and the time of the event, a path of 10 km that includes all the main places of the city, and sets as maximum number of partecipants 1000. The entries are soon sold out, and the run is a successfull event. The Mayor then decides to organize the event every year. \\ \\
\textbf{Scenario F} \\ \\
Steve loves sports. He is far from home for a business trip, but he knows that that day  will take place a city run, organized by the mayor of his city through Track4Run System. Then he downloads the app, and at the starting time, he selects the run from the live run list and follows it comfortable from his device. 




